```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
# Load libraries
library(tidyverse)
library(lubridate)
library(plotrix)
library(gridExtra)
library(grid)
library(ggmap)
library(ggrepel)
library(maps)
library(corrplot)
library(cowplot)
library(svMisc)
library(ggfortify)
library(AppliedPredictiveModeling)
library(caret)
library(knitr)
library(kableExtra)
library(ggpubr)

options(digits=3) # Change rounding to 3 digits

# Colorblind-friendly palette developed by IBM, 2, 4 and 5 color version
ibm2 <- c("#648FFF", "#ffb000")
ibm3 <- c("#DC267F", "#648FFF", "#FFB000")
ibm4 <- c("#785EF0", "#DC267F", "#FE6100", "#FFB000")
ibm5 <- c("#648FFF", "#785EF0", "#DC267F", "#FE6100", "#FFB000")
scalePal <- c("#565554","#B6C649","#785EF0")
pal3 <- c("#D84727","#FFB000","#2E4756")

```

```{r loadDatasets}
### Load site information
CAREER_sites <- read_csv("data/CAREER_SiteAttributes.csv")
CAREER_sites$date <- mdy(CAREER_sites$date)

### Load CAREER data matrix ####################################################
CAREERmatrix <- 
  read_csv(file = "data/CAREER_reachModeling.csv") %>%
  mutate(ER_daily_mean = abs(ER_daily_mean))
```

# Summary statistics

```{r mean and range}
## Nitrate ##
min(CAREERmatrix$NO2NO3_ugL, na.rm = T)
quantile(CAREERmatrix$NO2NO3_ugL, na.rm = T)
max(CAREERmatrix$NO2NO3_ugL, na.rm = T)
# Max NO3 stream
CAREERmatrix %>% select(SiteName, NO2NO3_ugL) %>% arrange(NO2NO3_ugL)

## DOC
quantile(CAREERmatrix$DOC_mgL, na.rm = T)

## Denitrification
# CAREER
max(CAREERmatrix$Denitrification_amended_mgNm2hr_mean, na.rm = T)
sd(CAREERmatrix$Denitrification_amended_mgNm2hr_mean, na.rm = T)
quantile(CAREERmatrix$Denitrification_amended_mgNm2hr_mean, na.rm = T) 
mean(CAREERmatrix$Denitrification_amended_mgNm2hr_mean, na.rm = T) 
sum(CAREERmatrix$Denitrification_amended_mgNm2hr_mean == 0, na.rm = T)

## Respiration
# CAREER
max(CAREERmatrix$ER_daily_mean, na.rm = T)
sd(CAREERmatrix$ER_daily_mean, na.rm = T)
quantile(CAREERmatrix$ER_daily_mean, na.rm = T)
mean(CAREERmatrix$ER_daily_mean, na.rm = T)

denit90 <- quantile(CAREERmatrix$Denitrification_amended_mgNm2hr_mean, 
                    na.rm = T, 0.9)
er90 <- quantile(CAREERmatrix$ER_daily_mean, na.rm = T, 0.9)
er10 <- quantile(CAREERmatrix$ER_daily_mean, na.rm = T, 0.1)

CAREERmatrix$Denitrification_amended_mgNm2hr_mean >= denit90 &
  CAREERmatrix$ER_daily_mean <= er10
sum(CAREERmatrix$Denitrification_amended_mgNm2hr_mean >= denit90 &
  CAREERmatrix$ER_daily_mean >= er90, na.rm = T)

# Strerams with 90th percentile denitrification
CAREERmatrix$ER_daily_mean[CAREERmatrix$Denitrification_amended_mgNm2hr_mean >=
  quantile(CAREERmatrix$Denitrification_amended_mgNm2hr_mean,na.rm = T, 0.9)]
CAREERmatrix$ER_daily_mean[CAREERmatrix$Denitrification_amended_mgNm2hr_mean >=
  quantile(CAREERmatrix$Denitrification_amended_mgNm2hr_mean,na.rm = T, 0.9)]

CAREERmatrix %>%
  filter(CAREERmatrix$ER_daily_mean < 1)
sum(!is.na(CAREERmatrix$ER_daily_mean))
```

# Conceptual figure for scale

```{r fig-conceptual-scale}
library(sf)
library(terra)
library(tidyterra)

# Load gray earth with shaded relief raster file from 
# https://www.naturalearthdata.com/downloads/10m-raster-data/10m-gray-earth/
relief_landscape <- rast("data/map/GRAY_HR_SR_OB_DR.tif")
# Crop raster to continental US
relief_landscape_crop <- terra::crop(relief_landscape, c(-131, -60, 20, 60), snap = "near")

# Load USGS raster file for BLDE elevation
relief_watershed <- rast("data/map/viz.USGS1m_hillshade_watershed_BLDE.tif")
# Change coordinate reference system
relief_watershed <- project(relief_watershed, "epsg:4326")

# Yellowstone aerial photo - for local scale
relief_YELL <- rast("data/map/2020_YELL_3_532000_4977000_image_greyscale.tif")
relief_YELL <- project(relief_YELL, "epsg:4326")

# Load NEON domains (downloaded from their arcGIS webpage)
domains <- 
  read_sf("data/map/NEONDomains/NEON_Domains.shp")
# Crop domains to continental US
domains_crop <- st_crop(domains, 
                        xmin = -131, xmax = -60, 
                        ymin = 50, ymax = 20)

# Load NEON watersheds (downloaded from their arcGIS webpage)
watersheds <- 
  read_sf("data/map/NEONAquaticWatershed/NEON_Aquatic_watershed.shp")
# Crop watersheds to Blacktail Deer
watersheds_crop <- watersheds[watersheds$SiteID == "BLDE",]

drain <- 
  read_sf("data/map/NEONAquaticWatershed/NEON_Aquatic_DrainageLine.shp")
drain_crop <- drain[drain$SiteID == "BLDE",]

# Load NEON aquatic reaches (downloaded from their arcGIS webpage)
reach <- 
  read_sf("data/map/NEONAquaticReach/Aquatic_StreamReach.shp")
# Crop to BLDE
reach_crop <- reach[reach$SiteID == "BLDE",]

# Continental map
#a <- 
  ggplot() +
  geom_spatraster(data = relief_landscape_crop, maxcell = 5e7) +
  geom_sf(data = filter(domains_crop, DomainID == 12), 
          color = "white", fill = NA, linewidth = 0.6, alpha = 0.2) +
  geom_sf(data = filter(domains_crop, DomainID == 12), 
          color = "#785EF0", fill = NA, linewidth = 0.4) +
  ggspatial::annotation_scale() +
  #scale_fill_viridis_c(option = "F") +
  scale_fill_continuous(palette = c( "grey20", "white")) +
  coord_sf(datum = sf::st_crs(4326), xlim = c(-129, -100), ylim = c(30, 55)) +
  theme_map() +
  theme(panel.border = element_rect(color = "black", fill = NA),
        legend.position = "none")
# Save
ggsave("outputs/figure_conceptual_continental_2.png", width = 2, height = 2, 
       units = "in", dpi = 500)

# Landscape map
#b <-
  ggplot() +
  #geom_spatraster(data = lidar_YELL) +
  geom_spatraster(data = relief_watershed) +
  geom_sf(data = drain_crop, color = "black", linewidth = 0.1, alpha = 0.3) +
  geom_sf(data = watersheds_crop, color = "white", fill = NA, 
          linewidth = 0.6, alpha = 0.2) +
  geom_sf(data = watersheds_crop, color = "#FE6100", fill = NA, 
          linewidth = 0.4) +
 # annotate("rect", xmin = -110.58, xmax = -110.595, 
  #              ymin = 44.8755, ymax = 44.8925, 
   #        color = "black", fill = "white", linewidth = 0.1) +
  #geom_sf(data = rivers_crop, color = "#648FFF", linewidth = 0.5) +
  ggspatial::annotation_scale() +
  scale_fill_continuous(palette = c("black", "white")) +
  coord_sf(datum = sf::st_crs(4326), 
           xlim = c(-110.66, -110.48), ylim = c(44.83, 44.97)
          ) +
  theme_map() +
  theme(panel.border = element_rect(color = "black", fill = NA),
        legend.position = "none")
# Save
ggsave("outputs/figure_conceptual_landscape_2.png", width = 2, height = 2, 
       units = "in", dpi = 500)

# Local map
#c <- 
  ggplot() +
  #geom_sf(data = rivers_crop, color = "#648FFF", linewidth = 0.5) +
  geom_spatraster_rgb(data = relief_YELL) +
  geom_sf(data = drain_crop, color = "black", linewidth = 0.2, alpha = 0.4) +
  geom_sf(data = reach_crop, color = "white", fill = NA, 
          linewidth = 0.8, alpha = 0.2) +
  geom_sf(data = reach_crop, color = "#FFB000", fill = NA, 
          linewidth = 0.5) +
  #geom_sf(data = thalweg,  color = "black") +
  ggspatial::annotation_scale() +
  coord_sf(datum = sf::st_crs(4326), 
           xlim = c(-110.592, -110.5825), ylim = c(44.9461, 44.9541)
           ) +
  theme_map() +
  #scale_fill_continuous(palette = c("black", "white")) +
  theme(panel.border = element_rect(color = "black", fill = NA),
        #legend.position = "none"
        )
# Save
ggsave("outputs/figure_conceptual_local_2.png", width = 2, height = 2, 
       units = "in", dpi = 500)

grid.arrange(a,b,c, nrow = 1)

ggplot() +
  geom_spatraster_rgb(data = relief_HOPB)
```

# Map

```{r Fig2 Map}
# Load urbnmapr package
#devtools::install_github("UrbanInstitute/urbnmapr")
library(urbnmapr)
library(sf)

# Get USA map
states_sf <- 
  urbnmapr::get_urbn_map("territories_states", sf = TRUE)
# Get world map
world.map <- map_data("world") 
# Get world oceans
ocean_sf <- 
  rnaturalearth::ne_download(scale = 10, type = "ocean", category = "physical")
# Get world lakes (big ones)
lake_sf <- 
  rnaturalearth::ne_download(scale = 10, type = "lakes", category = "physical")
# Load NEON domains (downloaded from their arcGIS webpage)
domains <- 
  sf::read_sf("data/map/NEONDomains/NEON_Domains.shp")

# Exclude the USA territories we don't want 
# (we want PR but not Hawaii, & not other territories)
states_contig <- 
  filter(states_sf, !(state_name %in% c("Hawaii", "Guam", "Virgin Islands", 
                                        "Mariana Islands", "American Samoa",
                                        "Alaska", "Puerto Rico")))

# Subset continental US domains
domains_contUS <-
  st_crop(domains, xmin = -130, xmax = -60, ymin = 20, ymax = 55) 
# Subset alaska domains
domains_AK <- 
  st_crop(domains, xmin = -180, xmax = -120, ymin = 50, ymax = 80)
# Subset PR domains
domains_PR <- 
  st_crop(domains, xmin = -70, xmax = -60, ymin = 10, ymax = 20)

# Transform site points into shape file
sites <- 
  CAREER_sites %>%
  select(SiteName, Longitude, Latitude) %>% 
  distinct() %>%
  mutate(SiteName = gsub(" River", " R.", SiteName),
         SiteName = gsub(" Creek", " Cr.", SiteName),
         SiteName = gsub(" Springs", " Spr.", SiteName),
         SiteName = gsub("South", "S.", SiteName),
         SiteName = gsub(" Brook", " Br.", SiteName),
         SiteName = gsub("Lower Knowton Fork ", "LKF ", SiteName)
         )

sites_sf <- 
  sites %>% 
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)

# Subset continental US sites
sites_cont <- st_crop(sites_sf, xmin = -130, xmax = -60, ymin = 20, ymax = 55) 
# Subset AK sites
sites_AK <- st_crop(sites_sf, xmin = -180, xmax = -120, ymin = 50, ymax = 80)
# Subset PR sites
sites_PR <- st_crop(sites_sf, xmin = -70, xmax = -60, ymin = 10, ymax = 20)

# Change projection of ocean
ocean_sf_2163 <- st_transform(ocean_sf, crs = 2163)
# Change projection of lakes
lake_sf_2163 <- st_transform(lake_sf, crs = 2163)

# Map continental US
a <-
  ggplot() +
  geom_sf(data = ocean_sf_2163, fill = "grey80", color = "grey80",
          linewidth = 0.1) +
  #geom_sf(data = states_contig) +
  geom_sf(data = domains_contUS, fill = "white", color = "grey80",
          linewidth = 0.2) +
    geom_sf(data = lake_sf_2163, fill = "grey60", color = NA,
          linewidth = 0.1) +
  # Point on site location
  geom_sf(data = sites_cont, shape = 16, size = 1, color = "black") +
  # Add site names
  geom_text_repel(data = sites_cont, 
                   stat = "sf_coordinates",
                  aes(label = SiteName, geometry = geometry), 
                  box.padding = 0.1, size = 2, segment.color = "black", 
                  max.overlaps = 80, min.segment.length = 0.1,
                  bg.color = "white", bg.r = 0.2) +
  ggspatial::annotation_scale() +
  scale_x_continuous(breaks = c(-110, -95, -80)) +
  scale_y_continuous(breaks = c(20, 30, 40, 50)) +
  coord_sf(datum = sf::st_crs(4326),
  xlim = c(-2E6, 2.6E6),
  ylim = c(-3E6, 1.6E6)) +
  labs(tag = "a") +
  #theme_map() +
  theme(panel.border = element_rect(color = "grey60", fill = "white"),
        axis.ticks = element_blank(),
        panel.background = element_rect(color ="white", fill = "grey95"),
        panel.grid = element_line(color = "white", linewidth = 0.25),
        plot.background = element_rect(color = "white", fill = "white"),
        axis.text = element_text(color = "grey30", size = 6),
        axis.title = element_blank(),
        legend.position = "none",
        legend.background = element_rect(color = NA, fill = NA),
        plot.tag.position = c(0.02, 0.96),
        plot.tag = element_text(face = "plain", size = 10))

# Map Alaska
b <- 
  ggplot() +
  geom_polygon(data = world.map, aes(x = long, y = lat, group = group),
               fill = "grey80", color = "grey80",
               linewidth = 0.1) +
  geom_sf(data = domains_AK, fill = "white", color = "grey80",
          linewidth = 0.2) +
  # Point on site location
  geom_sf(data = sites_AK, shape = 16, size = 1, color = "black") +
  # Add site names
  geom_text_repel(data = sites_AK, 
                   stat = "sf_coordinates",
                  aes(label = SiteName, geometry = geometry), 
                  box.padding = 0.1, size = 2, segment.color = "black", 
                  max.overlaps = 80, min.segment.length = 0.1,
                  bg.color = "white", bg.r = 0.2) +
  ggspatial::annotation_scale() +
  scale_x_continuous(breaks = c(-145, -160, -175)) +
  scale_y_continuous(breaks = c(50,60, 70)) +
  coord_sf(datum = sf::st_crs(4326), 
           xlim = c(-183, -134.5), 
           ylim = c(47, 78)) +
  scale_color_manual(values = c("grey10")) +
  labs(tag = "b") +
  theme_bw() +
  #theme_map() +
  theme(panel.border = element_rect(color = "grey60", fill = "white"),
        axis.ticks = element_blank(),
        panel.background = element_rect(color ="white", fill = "grey95"),
        panel.grid = element_line(color = "white", linewidth = 0.25),
        plot.background = element_rect(color = "white", fill = "white"),
        axis.text = element_text(color = "grey30", size = 6),
        axis.title = element_blank(),
        legend.position = "none",
        legend.background = element_rect(color = NA, fill = NA),
        plot.tag.position = c(0.05, 0.96),
        plot.tag = element_text(face = "plain", size = 10))

# Puerto Rico
c <- 
  ggplot() +
  geom_polygon(data = world.map, aes(x = long, y = lat, group = group),
               fill = "grey80", color = "grey80", linewidth = 0.1) +
  geom_sf(data = domains_PR, color = "grey60", fill = "white",
          linewidth = 0.2) +
  
  # Point on site location
  geom_sf(data = sites_PR, shape = 16, size = 1, color = "black") +
  # Add site names
  geom_text_repel(data = sites_PR, 
                   stat = "sf_coordinates",
                  aes(label = SiteName, geometry = geometry), 
                  box.padding = 0.1, size = 2, segment.color = "black", 
                  max.overlaps = 80, min.segment.length = 0.1,
                  bg.color = "white", bg.r = 0.2) +
  scale_x_continuous(breaks = c(-65, -66.5, -68)) +
  scale_y_continuous(breaks = c(17, 18)) +
  coord_sf(datum = sf::st_crs(4326), 
           xlim = c(-68.2, -64.9), 
           ylim = c(17, 19)) +
  ggspatial::annotation_scale() +
  labs(tag = "c") +
  scale_color_manual(values = c("grey10")) +
  #theme_map() +
  theme(panel.border = element_rect(color = "grey60", fill = "white"),
        axis.ticks = element_blank(),
        panel.background = element_rect(color ="white", fill = "grey95"),
        panel.grid = element_line(color = "white", linewidth = 0.25),
        plot.background = element_rect(color = "white", fill = "white"),
        axis.text = element_text(color = "grey30", size = 6),
        axis.title = element_blank(),
        legend.position = "none",
        legend.background = element_rect(color = NA, fill = NA),
        plot.tag.position = c(0.05, 0.9),
        plot.tag = element_text(face = "plain", size = 10))

layout_grid <- rbind(c(1,1,2),
                     c(1,1,2),
                     c(1,1,3))
grob <- grid.arrange(a,b,c, layout_matrix = layout_grid)
ggsave(grob, filename = "outputs/figure_map_sites.png", 
       width = 6, height = 4, bg = "white",
       units = "in", dpi = 1200)
```

# Denitrification and ER rates

```{r Fig3 denit & ER scatter}
## Denitrification ##
# Label points above a threshold
cutD <- quantile(CAREERmatrix$Denitrification_amended_mgNm2hr_mean, na.rm =T, 
                 probs = c(0.9)) # 90th percentile
cutER <- quantile(CAREERmatrix$ER_daily_mean, na.rm =T, probs = c(0.9)) # 90th percentile

## Scatterplot denit v. ER ##
ggplot(data = CAREERmatrix, aes(x = ER_daily_mean, 
                                  y = Denitrification_amended_mgNm2hr_mean)) +
  #geom_vline(aes(xintercept = cutER), linetype = 1, color = "#DC267F", 
   #          alpha = 0.5, linewidth = 0.25) +
  annotate("rect", xmin = cutER, xmax = Inf, ymin = -Inf, ymax = Inf,
           alpha = 0.1, fill = "#DC267F") +
  #geom_hline(aes(yintercept = cutD), linetype = 1, color = "#648FFF",
  #           alpha = 0.5, linewidth = 0.25) +
  annotate("rect", ymin = cutD, ymax = Inf, xmin = -Inf, xmax = Inf,
           alpha = 0.1, fill = "#648FFF") +
  ggpubr::stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "*`,`~")),
                   #label.x = log10(10), label.y = log10(50), 
                   label.x = 0, label.y = 16, 
                   size = 3.5, color = "grey10",  method = "spearman",
                   r.accuracy = 0.01, p.accuracy = 0.01) +
  # Labels
  geom_text_repel(aes(label = 
                         ifelse(Denitrification_amended_mgNm2hr_mean  >= cutD, 
                                SiteName, "")),
                   size = 3.5,
                   min.segment.length = unit(4, 'lines'),
                  color = "#648FFF", 
                  bg.color = "white", bg.r = 0.2) +
    geom_text_repel(aes(label = 
                         ifelse(ER_daily_mean  >= cutER, 
                                SiteName, "")),
                   size = 3.5,
                   min.segment.length = unit(4, 'lines'),
                  color = "#DC267F", 
                  bg.color = "white", bg.r = 0.2) +
  # Points
    geom_point(shape = 16, size = 2.5, alpha = 0.9, color = "grey60") +
    geom_point(data = filter(CAREERmatrix, Denitrification_amended_mgNm2hr_mean 
                             >= cutD), 
               shape = 16, size = 2.5,  color = "#648FFF") +
    geom_point(data = filter(CAREERmatrix, ER_daily_mean  >= cutER), 
               shape = 16, size = 2.5,  color = "#DC267F") +
  # Axis labels
  ylab(expression("Denitrification (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  xlab(expression("ER (g-"*"O"[2]~m^{-2}~"d"^{-1}*")")) +
  theme_minimal() +
  theme(axis.text = element_text(color = "grey10", size = 10),
        plot.tag = element_text(size = 10),
        panel.grid = element_line(linewidth = 0.25),
        axis.line =  element_line(color = "grey80", linewidth = 0.25),
        axis.title = element_text(size = 12),
        legend.position = "none",
        plot.margin=unit(rep(0.05,4), "in"))

ggsave(filename = "outputs/figure_denit-ER_boxplots_scatterplot.png",
       width = 4.5, height = 4.5, units = "in", dpi = 300)

## Get Spearman correlation info ###############################################
# Get paired data points only
cor_data <- 
  CAREERmatrix %>%
  select(ER_daily_mean, Denitrification_amended_mgNm2hr_mean) %>%
  filter(complete.cases(.))

cor.test(cor_data$ER_daily_mean,
           cor_data$Denitrification_amended_mgNm2hr_mean, 
           method = "spearman", exact = FALSE)
```

```{r Fig6 variableImportance denitrification}
library(emojifont)

# Load variable importance
modelResults <- 
  read_csv("data/predictiveModeling/DenitModeling_CAREER_2026-04-10.csv") %>%
  mutate(feature = recode(feature, 
                          K600_daily_mean = "K600",
                          SedCover_perc = "Sediment cover",
                          RockCover_perc = "Rock cover",
                          LandCover_Crop_perc = "Agricultural land",
                          DO_mgL_mean = "O₂",
                          NH4_ugL = "NH₄",
                          TransectDepth_Avg_cm = "Depth",
                          ER_daily_mean = "ER",
                          TDN_mgL = "TDN",
                          Mean_Slope = "Slope",
                          NO2NO3_ugL = "NO₂+NO₃",
                          LandCover_Built_perc = "Urban land",
                          Discharge_m3s = "Q",
                          VegCover_perc = "Macro. cover",
                          SRP_ugL = "SRP",
                          CanopyCover_Avg_perc = "Canopy cover",
                          SedimentCover_perc = "Sediment cover",
                          ReachWidth_Avg_m = "Stream width",
                          DIN_SRP = "DIN:SRP",
                          DOC_mgL = "DOC",
                          CWDCover_perc = "Woody cover",
                          WaterTemp_C_mean = "Temp.",
                          WatershedArea_km2 = "Watershed area",
                          TDN_TP = "TDN:TP"),
         feature = factor(feature, levels = feature)) %>%
  dplyr::arrange(desc(importance))

a <-
  ggplot(data = modelResults, aes(y = feature, x = importance)) +
  geom_point(size = 4, shape = 16, color = "#648FFF") +
  geom_linerange(aes(xmin = importance.05, xmax = importance.95),
                 color = "#648FFF") +
  labs(x = expression("Importance ("*Delta*"MSE)"), 
       tag = "a") +
  scale_y_discrete(limits = rev) +
  theme(legend.position = "none") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = c(0.7, 0.06),
        legend.key.size = unit(0.1, 'cm'),
        panel.grid.minor = element_blank(),
         axis.line =  element_line(color = "grey80", linewidth = 0.25),
        axis.title.y = element_blank(),
        panel.grid.major = element_line(linewidth = 0.25))

load("data/predictiveModeling/RWorkspace_DenitModeling_CAREER_2026-04-10.RData")

# Get partial dependence plots for important predictors
library(pdp)

uncenterscale <- function(transformed_data, orig_mean, orig_sd){
    transformed_data * orig_sd + orig_mean}

PDPplot <- function(varname, orig_data){
  # Compute
  partialout <-
    partial(mod_bestfit, pred.var = varname, 
            type = "regression")
  names(partialout) <- c("xvar", "yhat")
  
  # Get the reverse-transformed data variable
  meval <- mean(getElement(orig_data, varname), na.rm = TRUE) 
  sdval <- sd(getElement(orig_data, varname), na.rm = TRUE)
  
  partialout <-
    partialout %>%
    mutate(xvar_trans = uncenterscale(xvar, orig_mean = meval, orig_sd = sdval)) 
  
  plotout <-
    ggplot(data = partialout, aes(x = xvar_trans, y = yhat)) +
    geom_hline(yintercept = 0, color = "grey", linewidth = 0.1) +
    geom_rug(alpha = 0.5, sides = "l") +
    scale_y_continuous(limits = c(2,4.5), breaks = c(2,3,4)) +
    geom_line() +
    #stat_summary(fun.y = mean, geom = "line", color = "#519DAA",linetype = 2) +
    labs(x = varname#, y = expression(Delta*"Rate (%)")
         ) +
    theme_minimal() +
    theme(panel.grid.major = element_line(linewidth = 0.25),
          panel.grid.minor = element_blank())
  
  return(plotout)
}

b <-
  PDPplot("K600_daily_mean", data_denit) +
  geom_vline(xintercept = 0, color = "grey", linewidth = 0.1) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "b", x = expression(K[600]*" ("*d^{-1}*")"),
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))
  
c <-
  PDPplot("SedimentCover_perc", data_denit) +
  geom_vline(xintercept = 0, color = "grey", linewidth = 0.1) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "c", x = "Sediment cover (%)",
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

d <-
  PDPplot("RockCover_perc", data_denit) +
  geom_vline(xintercept = 0, color = "grey", linewidth = 0.1) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "d", x = "Rock cover (%)",
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

e <- 
  PDPplot("LandCover_Crop_perc", data_denit) +
  geom_vline(xintercept = 0, color = "grey", linewidth = 0.1) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "e", x = "Agricultural land (%)",
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

f <- 
  PDPplot("DO_mgL_mean", data_denit) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "f", x = expression(O[2]*" (mg "*L^{-1}*")"),
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

g <- 
  PDPplot("NH4_ugL", data_denit) +
  geom_vline(xintercept = 0, color = "grey", linewidth = 0.1) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "g", x = expression(NH[4]^{"+"}*" ("*mu*"g-N "*L^{-1}*")"),
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

h <- 
  PDPplot("DOC_mgL", data_denit) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "h", x = expression("DOC (mg "*L^{-1}*")"),
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

i <- 
  PDPplot("NO2NO3_ugL", data_denit) +
  geom_vline(xintercept = 0, color = "grey", linewidth = 0.1) +
  geom_rug(alpha = 0.5, sides = "l", color = "#648FFF") +
    geom_line(color = "#648FFF") +
  labs(tag = "i", x = expression(NO[2] + NO[3]^{"-"}*" ("*mu*"g-N "*L^{-1}*")"),
       y = expression("Rate (mg-N"~m^{-2}~"h"^{-1}*")"))

grob <- grid.arrange(a, b, c, d, e, f, g, h, i,
             layout_matrix = rbind(c(rep(1,3),rep(c(2,3),each = 2)),
                                   c(rep(1,3),rep(c(4,5),each = 2)),
                                   c(rep(1,3),rep(c(6,7),each = 2)),
                                   c(rep(1,3),rep(c(8,9),each = 2))))

ggsave(grob, filename = "outputs/figure_predmod_denitrif.png", width = 7, 
       height = 8, units = "in", dpi = 600)
```

```{r variable importance respiration}
library(emojifont)

# Load variable importance for ER
modelResults <- 
  read_csv("data/predictiveModeling/RespirationModeling_CAREER_2026-04-10.csv") %>%
  mutate(feature = recode(feature, 
                          RockCover_perc = "Rock cover",
                          LandCover_Built_perc = "Urban land",
                          Discharge_m3s = "Q",
                          VegCover_perc = "Macrophyte cover",
                          Mean_Slope = "Slope",
                          SedCover_perc = "Sediment cover",
                          Denitrification_amended_mgNm2hr_mean = "Denitrification",
                          LandCover_Crop_perc = "Agricultural land",
                          SRP_ugL = "SRP",
                          CanopyCover_Avg_perc = "Canopy cover",
                          DO_mgL_mean = "O₂",
                          SedimentCover_perc = "Sediment cover",
                          ReachWidth_Avg_m = "Stream width",
                          DIN_SRP = "DIN:SRP",
                          DOC_mgL = "DOC",
                          CWDCover_perc = "Woody cover",
                          WaterTemp_C_mean = "Temperature",
                          NH4_ugL = "NH₄",
                          TDN_mgL = "TDN",
                          WatershedArea_km2 = "Watershed area",
                          TDN_TP = "TDN:TP"),
         feature = factor(feature, levels = feature)) %>%
  dplyr::arrange(desc(importance))

a <-
  ggplot(data = modelResults, aes(y = feature, x = importance)) +
  geom_point(size = 4, shape = 16, color = "#DC267F") +
  geom_linerange(aes(xmin = importance.05, xmax = importance.95), 
                 color = "#DC267F") +
  labs(x = expression("Importance ("*Delta*"MSE)"), tag = "a") +
  scale_y_discrete(limits = rev) +
  theme(legend.position = "none") +
  theme_minimal() +
  coord_cartesian(xlim = c(-1, 6)) +
  theme(axis.title.y = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.06),
        legend.key.size = unit(0.05, 'cm'),
        panel.grid.minor = element_blank(),
        axis.line =  element_line(color = "grey80", linewidth = 0.25),
        panel.grid.major = element_line(linewidth = 0.25))

# Get partial dependence plots for important predictors
library(pdp)

uncenterscale <- function(transformed_data, orig_mean, orig_sd){
    transformed_data * orig_sd + orig_mean}

load("data/predictiveModeling/RWorkspace_RespirationModeling_CAREER_2026-04-10.RData")

PDPplot <- function(varname, orig_data){
  # Compute
  partialout <-
    partial(mod_bestfit, pred.var = varname, 
            type = "regression")
  names(partialout) <- c("xvar", "yhat")
  
  # Get the reverse-transformed data variable
  meval <- mean(getElement(orig_data, varname), na.rm = TRUE) 
  sdval <- sd(getElement(orig_data, varname), na.rm = TRUE)
  
  partialout <-
    partialout %>%
    mutate(xvar_trans = uncenterscale(xvar, orig_mean = meval, orig_sd = sdval)) 
  
  plotout <-
    ggplot(data = partialout, aes(x = xvar_trans, y = yhat)) +
    geom_hline(yintercept = 0, color = "grey", linewidth = 0.1) +
    geom_rug(alpha = 0.5, sides = "l") +
    geom_line() +
    scale_y_continuous(limits = c(6,8.5), breaks = c(6, 7, 8)) +
    #stat_summary(fun.y = mean, geom = "line", color = "#519DAA",linetype = 2) +
    labs(x = varname) +
    theme_minimal() +
    theme(panel.grid.major = element_line(linewidth = 0.25),
          panel.grid.minor = element_blank(),
          axis.line =  element_line(color = "grey80", linewidth = 0.25))
  
  return(plotout)
}

b <-
  PDPplot("RockCover_perc", data_er) +
  geom_rug(alpha = 0.5, sides = "l", color = "#DC267F") +
    geom_line(color = "#DC267F") +
  labs(tag = "b", x = expression("Rock cover (%)"),
       y = expression("Rate (g-"*O[2]~m^{-2}~"d"^{-1}*")"))

c <-
  PDPplot("VegCover_perc", data_er) +
  geom_rug(alpha = 0.5, sides = "l", color = "#DC267F") +
    geom_line(color = "#DC267F") +
  labs(tag = "c", x = expression("Macrophyte cover (%)"),
       y = expression("Rate (g-"*O[2]~m^{-2}~"d"^{-1}*")"))

d <- 
  PDPplot("Discharge_m3s", data_er) +
  geom_rug(alpha = 0.5, sides = "l", color = "#DC267F") +
    geom_line(color = "#DC267F") +
  labs(tag = "d", x = expression("Discharge ("*m^3 ~ s^{-1}*")"),
       y = expression("Rate (g-"*O[2]~m^{-2}~"d"^{-1}*")"))

grob <- grid.arrange(a, b, c, d, 
             layout_matrix = rbind(c(1,1,1,2,2),
                                   c(1,1,1,3,3),
                                   c(1,1,1,4,4)))

ggsave(grob, filename = "outputs/figure_predmod_ER.png", width = 5, 
       height = 6, units = "in", dpi = 600)
```



# Plot of denitrification impacted by ER and ecoregion to address hyp 3?

```{r rates & substrate heterogenity}
ggplot(data = CAREERmatrix, 
       aes(x = simpsonsInfo, y = Denitrification_amended_mgNm2hr_mean)) +
  # Add regression line eqn and R2
  ggpubr::stat_regline_equation(label.x = 1, label.y = 15, size = 3) +
  ggpubr::stat_cor(label.x = 1, label.y = 14, size = 3) +
  geom_smooth(method = "lm", color = "black", fullrange = T, se = F) +
  stat_smooth(method = "lm", color = "black", geom = "ribbon", fill = NA, 
              fullrange = T, linetype = 2) +
  geom_point(fill = ibm4[1], color = "black", size = 5, shape = 21) +
   # Labels
  geom_label_repel(aes(label = ifelse(Denitrification_amended_mgNm2hr_mean >= cutD, 
                                      SiteName, "")),
                   #nudge_x = 1, nudge_y = 1, 
                   size = 3,
                   min.segment.length = unit(0, 'lines')) +
  # Axis labels and scales
  xlab(expression("Simpson's information index")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "a") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

ggplot(data = CAREERmatrix, 
       aes(x = simpsonsInfo, y = ER_mean)) +
  ggpubr::stat_regline_equation(label.y = 8, size = 5) +
  ggpubr::stat_cor(label.y = 7, size = 5) +
  geom_point(fill = ibm4[1], color = "black", size = 5, shape = 21) +
  # Axis labels and scales
  xlab(expression("Simpson's information index")) +
  ylab(expression("Ecosystem respiration rate (g-"*O[2]~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "a") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

ggplot(data = CAREERmatrix, aes(x = shannonsEvenness, 
                                y = Denitrification_amended_mgNm2hr_mean, fill = Study)) +
  ggpubr::stat_regline_equation(label.y = 8, size = 5) +
  ggpubr::stat_cor(label.y = 7.3, size = 5) +
  geom_smooth(method = "lm", color = "black", fullrange = T, se = F) +
  stat_smooth(method = "lm", color = "black", geom = "ribbon", fill = NA, 
              fullrange = T, linetype = 2) +
  geom_point(color = "black", size = 5, shape = 21) +
  # Axis labels and scales
  xlab(expression("Shannon's evenness")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  coord_cartesian(ylim = c(0, 16)) +
  labs(tag = "a") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

ggplot(data = CAREERmatrix, aes(x = shannonsEvenness, 
                                y = abs(ER_mean), fill = Study)) +
  ggpubr::stat_regline_equation(label.y = 8, size = 5) +
  ggpubr::stat_cor(label.y = 7.3, size = 5) +
  geom_point(color = "black", size = 5, shape = 21) +
  # Axis labels and scales
  xlab(expression("Shannon's evenness")) +
  ylab(expression("Ecosystem respiration rate (g-"*O[2]~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "a") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        strip.text = element_text(size = 14),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 
```

```{r Fig_S1 scatterplot comparisons}
### Keep for CAREER paper, leave out of your dissertation ###
### Scatterplots with lit review data ##########################################
## Compile data to run linear models
# Denitrification metadataset
denitMeta <- 
  CAREERmatrix %>%
  select(SiteName, ER_mean, DenitAmended_Mean_mgNm2hr, DOC_mgL, NO2NO3_ugL) %>%
  mutate(ER_mean = abs(ER_mean)) %>%
  rename(ER_Mean_gO2m2d = ER_mean, Denit_Mean_mgNm2hr=DenitAmended_Mean_mgNm2hr,
         NO3_Mean_ugNL = NO2NO3_ugL) %>%
  full_join(., LINXII %>% select(SiteName, ER_Mean_gO2m2d, Denit_Mean_mgNm2hr, 
                                 DOC_Mean_mgL,NO3_Mean_ugNL))

# Linear trend
model <- lm(log(Denit_Mean_mgNm2hr)~log(ER_Mean_gO2m2d), 
            subset(denitMeta, Denit_Mean_mgNm2hr > 0))
#summary(model) #log-log relationship, log(y) = a + b log(x)
model <- lm(log(Denit_Mean_mgNm2hr+1)~log(ER_Mean_gO2m2d+1), denitMeta)
#summary(model) #log-log relationship, log(y) = a + b log(x)
#formula(model)
#coefficients(model)

# Nitrate vs denitrification
#a <- 
  ggplot(data = NULL) +
  # Trendline
  geom_smooth(data = denitMeta, aes(x = NO3_Mean_ugNL, y = Denit_Mean_mgNm2hr), 
              method = "lm", color = "black") +
  # Career sites
  geom_point(data = CAREERmatrix, 
             aes(x = NO2NO3_ugL, y = DenitAmended_Mean_mgNm2hr, 
                          fill = "Nationwide survey"), size = 3, 
             shape = 21, alpha = 0.7) +
  # LINXII
  geom_point(data = LINXII, aes(x = NO3_Mean_ugNL, y = Denit_Mean_mgNm2hr, 
                          fill = "Mulholland et al. 2009"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Marcarelli 2008
  geom_point(data = subset(Marcarelli, RateType == "Denitrification"), 
             aes(x = Nitrate_ugNL, y = rate_ugNm2hr/1000, 
                          fill = "Marcarelli et al. 2008"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Add trendline equation
  ggpubr::stat_cor(data = denitMeta, aes(x = NO3_Mean_ugNL, y = Denit_Mean_mgNm2hr),
                   label.x.npc = 0, label.y.npc = 0.98) +
  ggpubr::stat_regline_equation(data = denitMeta, aes(x = NO3_Mean_ugNL, y = Denit_Mean_mgNm2hr),
                                label.x.npc = 0, label.y.npc = 0.92) +
  # Axis labels and scales
  scale_x_log10() +
  scale_y_log10(breaks=c(0.001,0.1, 10, 1000)) +
  coord_cartesian(ylim = c(1E-5, 1000)) +
  xlab(expression("Nitrate ("*mu*"g-N L"^{-1}*")")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_fill_manual(values = c("Nationwide survey" = ibm4[1], 
                               "Mulholland et al. 2009" = ibm4[2], 
                               "Marcarelli et al. 2008" = ibm4[3])) +
  theme_classic() +
  labs(tag = "a", fill = "Study") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        #legend.position = c(0.2,0.2),
        legend.background = element_rect(color = "black"),
        legend.key.size = unit(0.15, 'in')) 

# ER vs Denit
ggplot(data = NULL) +
  # Trendline
  geom_smooth(data = denitMeta, aes(x = ER_Mean_gO2m2d, y = Denit_Mean_mgNm2hr), 
              method = "lm", color = "black") +
  # Career sites
  geom_point(data = CAREERmatrix, 
             aes(x = abs(ER_mean), y = DenitAmended_Mean_mgNm2hr, 
                          fill = "Nationwide survey"), size = 3, 
             shape = 21, alpha = 0.7) +
  # LINXII
  geom_point(data = LINXII, aes(x = ER_Mean_gO2m2d, y = Denit_Mean_mgNm2hr, 
                          fill = "Mulholland et al. 2009"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Add trendline equation
  ggpubr::stat_cor(data = denitMeta, aes(x = ER_Mean_gO2m2d, y = Denit_Mean_mgNm2hr),
                   label.x.npc = 0, label.y.npc = 0.98) +
  ggpubr::stat_regline_equation(data = denitMeta, aes(x = ER_Mean_gO2m2d, y = Denit_Mean_mgNm2hr),
                                label.x.npc = 0, label.y.npc = 0.92) +
  # Axis labels and scales
  scale_x_log10() +
  scale_y_log10(breaks=c(0.001,0.1, 10, 1000), labels = c("0.001","0.1", "10", "1,000")) +
  coord_cartesian(ylim = c(1E-5, 1000)) +
  xlab(expression("Ecosystem respiration (mg-O2"~m^{-2}~"hr"^{-1}*")")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_fill_manual(values = c("Nationwide survey" = ibm4[1], 
                               "Mulholland et al. 2009" = ibm4[2], 
                               "Marcarelli et al. 2008" = ibm4[3])) +
  theme_classic() +
  labs(fill = "Study", tag= "b") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = c(0.25,0.15),
        legend.background = element_rect(color = "black"),
        legend.key.size = unit(0.15, 'in')) 
ggsave(a, filename = "plots/ESCPoster/ER_Denit_Scatter.png", height = 5, 
       width = 5, units = "in", dpi = 300)

```

```{r Regime comparison with rates}
# Order er regimes chronologically
plotMetab$ERCluster <- 
  factor(plotMetab$ERCluster, levels = c("Aseasonal/Stochastic", "Summer Peak",
                                       "Summer-Fall Plateau", 
                                       "Summer-Fall Valley", "Fall Peak"))
greyCells <- 
  data.frame(GPPCluster = c(rep("Summer-Fall Valley", 4),
                            "Summer Peak", rep("Spring Peak", 2)),
             ERCluster = c("Aseasonal/Stochastic", "Summer Peak",
                           "Summer-Fall Plateau", "Fall Peak",
                           "Summer-Fall Valley", "Summer-Fall Valley",
                           "Fall Peak")) %>%
  mutate(GPPCluster = factor(GPPCluster, levels = c("Spring Peak", "Summer Peak",
                                                    "Summer-Fall Valley")),
         ERCluster = factor(ERCluster, levels = c("Aseasonal/Stochastic", 
                                                  "Summer Peak",
                                                  "Summer-Fall Plateau", 
                                       "Summer-Fall Valley", "Fall Peak")))
comboNums <- data.frame(GPPCluster = c(rep(c("Spring Peak", "Summer Peak"), 3),
                                       "Summer-Fall Valley",
                                       "Summer Peak"),
                        ERCluster = c(rep("Aseasonal/Stochastic", 2),
                                      rep("Summer Peak", 2),
                                      rep("Summer-Fall Plateau", 2),
                                      "Summer-Fall Valley",
                                      "Fall Peak"),
                        number = paste0(1:8, "."), xpos = ymd("2001-01-30"),
                        ypos = 20) %>%
  mutate(GPPCluster = factor(GPPCluster, levels = c("Spring Peak", "Summer Peak",
                                                    "Summer-Fall Valley")),
         ERCluster = factor(ERCluster, levels = c("Aseasonal/Stochastic", 
                                                  "Summer Peak",
                                                  "Summer-Fall Plateau", 
                                       "Summer-Fall Valley", "Fall Peak")))
clusterList <- 
  plotMetab %>%
  select(SiteYear, ERCluster, GPPCluster) %>%
  distinct %>%
  mutate(xpos = ymd("2001-03-30"), ypos = 20)


a <-
  ggplot(data = plotMetab) +
  facet_grid(rows = vars(ERCluster), cols = vars(GPPCluster), switch = "y") +
  # Shade out NA cells
  geom_rect(data = greyCells, aes(xmin = as.Date(-Inf), xmax = as.Date(Inf), 
                ymin = -Inf, ymax = Inf), 
    fill = 'lightgrey', alpha = 0.5) +
  geom_hline(aes(yintercept = 0)) +
  # Add annotation numbers
  geom_text_repel(data = clusterList, aes(x = xpos, y = ypos, 
                                           label = SiteYear), size = 3,
                  box.padding = 0, min.segment.length = Inf,
                  direction = "y") +
  #geom_text(data = comboNums, aes(x = xpos, y = ypos, label = number)) +
  # Add GPP GAMs
  geom_line(aes(x = DOYDate, y = GPP_GAM, group = SiteYear), 
            color = ibm5[1], linewidth = 1,
            alpha = 0.9) +
  # Add ER GAMs
  geom_line(aes(x = DOYDate, y = ER_GAM, group = SiteYear), color = ibm5[3],
            linewidth = 1, alpha = 0.9) +
  # Theming
  scale_x_date(breaks = "2 months", date_labels = "%b") +
  coord_cartesian(ylim = c(-25,25)) +
  ylab(expression("GPP or ER (g"~O[2]~m^2~"d"^{-1}*")")) +
  xlab("Date") +
  # Remove legend for site
  guides(color = "none", linetype = guide_legend(nrow = 3, title = "Year")) +
  labs(tag = "a") +
  # Theme adjustments
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(size = 10),
        strip.text = element_text(size = 10, color = "white", face = "bold"),
        strip.background.x = element_rect(fill = paste0(ibm5[1])),
        strip.background.y = element_rect(fill = paste0(ibm5[3])),
        panel.background = element_rect(color = "black"), 
        legend.position = "none")

ggsave(filename = "plots/regimeGrid.png", height = 9, 
       width = 7.5, units = "in", dpi = 600)


ggplot(data = CAREERLINXIImatrix, aes(y = abs(GPP_Mean_gO2m2d), 
                                      x = Denit_Mean_mgNm2hr)) +
  # Add regression line eqn and R2
  ggpubr::stat_regline_equation(label.x = 0.001, label.y = 18, size = 3) +
  ggpubr::stat_cor(label.x = 0.001, label.y = 16, size = 3) +
  geom_smooth(method = "lm", color = "black", fullrange = T, se = F) +
  stat_smooth(method = "lm", color = "black", geom = "ribbon", fill = NA, 
              fullrange = T, linetype = 2) +
  
  # Labels
  geom_label_repel(aes(label =  SiteName),
                   nudge_x = 1, nudge_y = 1, 
                   size = 3,
                   min.segment.length = unit(0, 'lines')) +
  # Points
  geom_point(aes(fill = Study), shape = 21, size = 2.5) +
  # Axis labels
  xlab(expression("Denitrification (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  ylab(expression("GPP (g-"*"O"[2]~m^{-2}~"d"^{-1}*")")) +
  scale_fill_manual(values = c(ibm5[3], ibm5[1])) +
  labs(tag = "c") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        plot.tag = element_text(size = 8),
        axis.title = element_text(size = 10),
        panel.background = element_rect(color = "black"), 
        legend.position = "none",
        plot.margin=unit(rep(0.05,4), "in"))

ggplot(data = CAREERLINXIImatrix, aes(y = abs(GPP_Mean_gO2m2d), 
                                      x = abs(ER_Mean_gO2m2d))) +
  # Add regression line eqn and R2
  ggpubr::stat_regline_equation(label.x = 0.001, label.y = 18, size = 3) +
  ggpubr::stat_cor(label.x = 0.001, label.y = 16, size = 3) +
  geom_smooth(method = "lm", color = "black", fullrange = T, se = F) +
  stat_smooth(method = "lm", color = "black", geom = "ribbon", fill = NA, 
              fullrange = T, linetype = 2) +
  
  # Labels
  geom_label_repel(aes(label =  SiteName),
                   nudge_x = 1, nudge_y = 1, 
                   size = 3,
                   min.segment.length = unit(0, 'lines')) +
  # Points
  geom_point(aes(fill = Study), shape = 21, size = 2.5) +
  # Axis labels
  xlab(expression("ER (g-"*"O"[2]~m^{-2}~"d"^{-1}*")")) +
  ylab(expression("GPP (g-"*"O"[2]~m^{-2}~"d"^{-1}*")")) +
  scale_fill_manual(values = c(ibm5[3], ibm5[1])) +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        plot.tag = element_text(size = 8),
        axis.title = element_text(size = 10),
        panel.background = element_rect(color = "black"), 
        legend.position = "none",
        plot.margin=unit(rep(0.05,4), "in"))

```

```{r Fig S3 Individual metab plots}
### Annual metabolism time series ##############################################
suppMetab <-
  CAREER_metabolism %>%
  mutate(DOY = yday(date),
         DOYDate = as.Date(DOY, origin = "2000-12-31"),
         SiteYear = paste0(SiteName, ", ",year(date))) %>%
  filter(DOY != 366 & DOY != 365 & DOY != 1) %>%
# Create dummy max and min dates for plotting x limits
  group_by(SiteYear) %>%
  mutate(xmin = ymd(paste0(unique(year(date)), "-01-01")),
         xmax = ymd(paste0(unique(year(date)), "-12-31")))

# Grab site name, data, Arrange sites by longitude
siteOrder <-
  CAREER_sites %>% 
  arrange(Longitude) %>%
  # Preserve sites that we have metabolism estimates for
  filter(SiteName %in% unique(CAREER_metabolism$SiteName)) %>%
  # Create SiteYear column
  mutate(SiteYear = paste(SiteName, year(date), sep = ", "),
         SiteYear = factor(SiteYear, levels = unique(SiteYear))) %>%
  filter(SiteYear != "Pilgrim River, 2019")

# Plot
ggplot(data = suppMetab) +
  facet_wrap(vars(SiteYear), ncol = 2, scales = "free_x") +
  # dummy blank layers to define min and max dates for x axis
  geom_blank(aes(x = xmin)) + geom_blank(aes(x = xmax)) +
  # y-axis
  geom_hline(aes(yintercept = 0)) +
  # Vertical line on N sampling date
  geom_vline(data = siteOrder, aes(xintercept = date), linetype = 2) +
  # GAM gpp
  geom_ribbon(aes(x = date, ymin = GPP_GAM-GPP_GAMse, 
                  ymax = GPP_GAM+GPP_GAMse), fill = ibm5[1], alpha = 0.5) +
  geom_line(aes(x = date, y = GPP_GAM), color = ibm5[1], linewidth = 1.5) +
  # GAM er
  geom_ribbon(aes(x = date, ymin = ER_GAM-ER_GAMse, 
                  ymax = ER_GAM+ER_GAMse), fill = ibm5[3], alpha = 0.5) +
  geom_line(aes(x = date, y = ER_GAM), color = ibm5[3], linewidth = 1.5) +
  # Add points
  geom_point(aes(x = date, y = GPP_mean), color = ibm5[1], 
             shape = 21, fill = "white") +
  geom_point(aes(x = date, y = ER_mean), color = ibm5[3], 
             shape = 21, fill = "white") +
  scale_x_date(breaks = "1 month", date_labels = "%b") +
  coord_cartesian(ylim = c(-25,25)) +
  ylab(expression("GPP or ER (g"~O[2]~m^2~"d"^{-1}*")")) +
  xlab("Date") +
  # Remove legend for site
  guides(color = "none", linetype = guide_legend(nrow = 3, title = "Year")) +
  # Theme adjustments
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(size = 10),
        strip.text = element_text(size = 10),
        panel.background = element_rect(color = "black"), 
        legend.position = "none")

# Save plot
ggsave(filename = "plots/supplemental/annualMetabolism.png", height = 25, 
       width = 7.5, units = "in", dpi = 600)
```

```{r ratesBySite, fig.height=7, fig.width = 15, fig.fullwidth = T}
CAREER_wholeReach_long <- 
  CAREER_wholeReach %>%
  select(SiteName, date, Longitude, DenitAmended_Mean_mgNm2hr:Nfix_SD_mgNm2hr) %>%
  pivot_longer(names_to = c("process", "stat", "unit"), 
               names_pattern = "(\\w+)_(\\w+)_(\\w+)",
               cols = DenitAmended_Mean_mgNm2hr:Nfix_SD_mgNm2hr) %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  mutate(MeanPlusSD = Mean + SD,
         MeanMinusSD = Mean - SD)

# Rename fixation and denitrification
CAREER_wholeReach_long$process <- recode(CAREER_wholeReach_long$process, 
                                         "Nfix" = "N Fixation",
                                         "DenitAmended" = "Denitrification")
#Factorize site name by latitude
CAREER_wholeReach_long$SiteName <- reorder(CAREER_wholeReach_long$SiteName, 
                                           CAREER_wholeReach_long$Longitude)

mean(CAREER_wholeReach$DenitAmended_Mean_mgNm2hr, na.rm = T)
mean(CAREER_wholeReach$Nfix_Mean_mgNm2hr, na.rm = T)

a <- 
  ggplot(data = subset(CAREER_wholeReach_long, process %in% c("Denitrification", 
                                                              "N Fixation")),
       aes(y = Mean, x = process, fill = process)) +
  geom_jitter(color = "black", size = 2, width = 0.2, shape = 21, alpha = 0.7) +
  # Add a point for the means
  stat_summary(fun = mean, geom = "point", shape = 24, size = 4, fill = "white") +
  # Axis labels and scales
  xlab(expression("Process")) +
  ylab(expression("Rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "a") +
  scale_fill_manual(values = c(ibm5[4], ibm5[1])) +
  scale_y_continuous(labels = c("0","5","10","15"),  breaks = c(0, 5, 10, 15)) +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

b <- 
  ggplot(data = CAREER_wholeReach,
       aes(x = Nfix_Mean_mgNm2hr, y = DenitAmended_Mean_mgNm2hr)) +
  geom_point(size = 2, shape = 21) +
  # Add 1:1 line
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  # Axis labels and scales
  scale_x_log10(labels = c("0.00001","0.001","0.1", "10"), 
                breaks = c(1E-5,0.001, 0.1, 10)) +
  scale_y_log10(labels = c("0.1", "1","10"), 
                breaks = c(0.1, 1, 10)) +
  xlab(expression("N fixation rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "b") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

#### Plot whole-reach rates by site ###########################################
# Factorize site name by 

c <- 
  ggplot(data = subset(CAREER_wholeReach_long, 
                       process %in% c("Denitrification", "N Fixation")), 
         aes(y = SiteName)) +
  facet_wrap(~ process) +
  # Line segment at each site name
  geom_segment(aes(y= SiteName, yend = SiteName, x = 1E-7, xend = 100), 
               color = "lightgrey") +
  # Add error bars
  geom_errorbar(aes(xmin = pmax(0, MeanMinusSD), xmax = MeanPlusSD),
                width = 0.8, position = position_dodge2(width = 0.8),
                size = 0.6) +
  geom_point(aes(x = Mean, fill = process),
             size = 2.5, shape = 21,
             position = position_dodge2(width = 0.8)) +
  # Axis labels and scales
  ylab(expression("Site")) +
  xlab(expression("Rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_x_log10(labels = c("0.00001","0.001","0.1", "10"), 
                breaks = c(1E-5,0.001, 0.1, 10)) +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(values = c(ibm5[4], ibm5[1])) +
  coord_cartesian(xlim = c(1E-6, 30)) +
  labs(tag = "c") +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none")

# Arrange plot
grob <- grid.arrange(a, b, c, 
                     layout_matrix = rbind(c(1,3,3,3),
                                           c(2,3,3,3)))
# Save
ggsave(grob, filename = "plots/ReachRates_ByStream_horizontal.png",
       width = 11, height = 6, units = "in", dpi = 300)
```

# Denitrification and fixation rates in our study compared to literature

```{r literature, fig.cap="Comparison of reach-scaled denitrification rates (a) and nitrogen fixation rates (b) from this study with published rates from Mulholland et al. 2009 and Marcarelli et al. 2008.", fig.height=5, fig.width=10, fig.fullwidth = TRUE}
# Load marcarelli data
Marcarelli <- read_csv(file = "data/litReview/Marcarelli_2008litreviewrates.csv")

options(scipen=10000)

#### Compile data to run linear models #########################################
# Denitrification metadataset
denitMeta <- CAREER_wholeReach %>%
  select(SiteName, NO2NO3_ugL, DenitAmended_Mean_mgNm2hr) %>%
  rename(NO3_ugNL = NO2NO3_ugL, 
         Denit_mgNm2hr = DenitAmended_Mean_mgNm2hr)
denitMeta <- full_join(denitMeta, 
                       LINXII %>% select(SiteName, NO3_ugNL, Denit_mgNm2hr))
denitMeta <- 
  subset(Marcarelli, RateType == "Denitrification") %>% 
  select(Stream, Nitrate_ugNL, rate_ugNm2hr) %>%
  mutate(Denit_mgNm2hr = rate_ugNm2hr/1000) %>%
  rename(SiteName = Stream, NO3_ugNL = Nitrate_ugNL) %>%
  select(SiteName, NO3_ugNL, Denit_mgNm2hr) %>%
  full_join(., denitMeta)
# Linear trend
model <- lm(log(Denit_mgNm2hr)~log(NO3_ugNL), subset(denitMeta, Denit_mgNm2hr > 0))
#summary(model) #log-log relationship, log(y) = a + b log(x)
model <- lm(log(Denit_mgNm2hr+1)~log(NO3_ugNL+1), denitMeta)
#summary(model) #log-log relationship, log(y) = a + b log(x)
#formula(model)
#coefficients(model)

# N fixation metadataset
nfixMeta <- 
  CAREER_wholeReach %>%
  select(SiteName, NO2NO3_ugL, Nfix_Mean_mgNm2hr) %>%
  rename(NO3_ugNL = NO2NO3_ugL, 
         Nfix_mgNm2hr = Nfix_Mean_mgNm2hr)
nfixMeta <- subset(Marcarelli, RateType == "N fixation") %>% 
  select(Stream, Nitrate_ugNL, rate_ugNm2hr) %>%
  mutate(Nfix_mgNm2hr = rate_ugNm2hr/1000) %>%
  rename(SiteName = Stream, NO3_ugNL = Nitrate_ugNL) %>%
  select(SiteName, NO3_ugNL, Nfix_mgNm2hr) %>%
  full_join(., nfixMeta)

# Linear trend
model <- lm(log(Nfix_mgNm2hr+1)~log(NO3_ugNL+1), nfixMeta)
summary(model)

# Plot
a <- 
  ggplot(data = NULL) +
  # Trendline
  geom_smooth(data = denitMeta, aes(x = NO3_ugNL, y = Denit_mgNm2hr), 
              method = "lm", color = "black") +
  # Career sites
  geom_point(data = CAREER_wholeReach, 
             aes(x = NO2NO3_ugL, y = DenitAmended_Mean_mgNm2hr, 
                          fill = "This study"), size = 3, 
             shape = 21, alpha = 0.7) +
  # LINXII
  geom_point(data = LINXII, aes(x = NO3_ugNL, y = Denit_mgNm2hr, 
                          fill = "Mulholland et al. 2009"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Marcarelli 2008
  geom_point(data = subset(Marcarelli, RateType == "Denitrification"), 
             aes(x = Nitrate_ugNL, y = rate_ugNm2hr/1000, 
                          fill = "Marcarelli et al. 2008"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Add trendline equation
  ggpubr::stat_cor(data = denitMeta, aes(x = NO3_ugNL, y = Denit_mgNm2hr),
                   label.x.npc = 0, label.y.npc = 0.98) +
  ggpubr::stat_regline_equation(data = denitMeta, aes(x = NO3_ugNL, y = Denit_mgNm2hr),
                                label.x.npc = 0, label.y.npc = 0.92) +
  # Axis labels and scales
  scale_x_log10() +
  scale_y_log10(breaks=c(0.001,0.1, 10, 1000)) +
  coord_cartesian(ylim = c(1E-5, 1000)) +
  xlab(expression("Nitrate ("*mu*"g-N L"^{-1}*")")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_fill_manual(values = c("This study" = ibm4[1], "Mulholland et al. 2009" = ibm4[2], 
                               "Marcarelli et al. 2008" = ibm4[3])) +
  theme_classic() +
  labs(tag = "a", fill = "Study") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = c(0.25,0.15),
        legend.background = element_rect(color = "black"),
        legend.key.size = unit(0.15, 'in')) 


# N fixation
b <- 
  ggplot(data = NULL) +
  # Marcarelli review
  geom_point(data = subset(Marcarelli, RateType == "N fixation"), 
             aes(x = Nitrate_ugNL, y = rate_ugNm2hr/1000, 
                          fill = "Marcarelli et al. 2008"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Career sites
  geom_point(data = CAREER_wholeReach, 
             aes(x = NO2NO3_ugL, y = Nfix_Mean_mgNm2hr, 
                          fill = "This study"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Nitrate ("*mu*"g-N L"^{-1}*")")) +
  ylab(expression("Nitrogen fixation rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_fill_manual(values = c("This study" = ibm4[1], 
                               "Mulholland et al. 2009" = ibm4[2], 
                               "Marcarelli et al. 2008" = ibm4[3])) +
  # Log scale
  scale_x_log10() +
  scale_y_log10() +
  coord_cartesian(ylim = c(1E-6, 1000)) +
  # Theme adjustments
  theme_classic() +
  labs(tag = "b", fill = "Study") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = c(0.75, 0.85),
        legend.background = element_rect(color = "black"),
        legend.key.size = unit(0.15, 'in')) 

grob3 <- grid.arrange(a, b, nrow = 1)
ggsave(grob3, filename = "plots/NO3_DenitNfix_Scatter.png", height = 5, 
       width = 10, units = "in", dpi = 300)
```

## Without CAREER points (for slideshows)

```{r LitReviewNvsRates_sansCAREER, fig.cap="Reach-scaled denitrification rates (a) and nitrogen fixation rates (b) from Mulholland et al. 2009 and Marcarelli et al. 2008.", fig.height=5, fig.width=10, fig.fullwidth = TRUE}
# Same scatterplot without CAREER data, for a talk Amy is giving
# Denitrification metadataset
a2 <- 
  ggplot(data = NULL) +
  # LINXII
  geom_point(data = LINXII, aes(x = NO3_ugNL, y = Denit_mgNm2hr, 
                          fill = "Mulholland et al. 2009"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Marcarelli 2008
  geom_point(data = subset(Marcarelli, RateType == "Denitrification"), 
             aes(x = Nitrate_ugNL, y = rate_ugNm2hr/1000, 
                          fill = "Marcarelli et al. 2008"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Add trendline equation
  #ggpubr::stat_cor(data = denitMeta, aes(x = NO3_ugNL, y = Denit_mgNm2hr),
  #                 label.x.npc = 0, label.y.npc = 0.9) +
  #ggpubr::stat_regline_equation(data = denitMeta, aes(x = NO3_ugNL, y = Denit_mgNm2hr),
  #                              label.x.npc = 0, label.y.npc = 0.85) +
  # Axis labels and scales
  scale_x_log10() +
  scale_y_log10(breaks=c(0.001,0.1, 10, 1000)) +
  coord_cartesian(ylim = c(1E-5, 1000)) +
  xlab(expression("Nitrate ("*mu*"g-N L"^{-1}*")")) +
  ylab(expression("Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_fill_manual(values = c("Mulholland et al. 2009" = ibm4[2], 
                               "Marcarelli et al. 2008" = ibm4[3])) +
  theme_classic() +
  labs(tag = "a", fill = "Study") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none",
        legend.background = element_rect(color = "black"),
        legend.key.size = unit(0.15, 'in')) 

b2 <- 
  ggplot(data = NULL) +
  # Marcarelli review
  geom_point(data = subset(Marcarelli, RateType == "N fixation"), 
             aes(x = Nitrate_ugNL, y = rate_ugNm2hr/1000, 
                          fill = "Marcarelli et al. 2008"), size = 3, 
             shape = 21, alpha = 0.7) +
  # Add trendline equation
  #ggpubr::stat_cor(data = nfixMeta, aes(x = NO3_ugNL, y = Nfix_mgNm2hr),
  #                 label.x.npc = 0, label.y.npc = 1) +
  #ggpubr::stat_regline_equation(data = nfixMeta, aes(x = NO3_ugNL, y = Nfix_mgNm2hr),
  #                              label.x.npc = 0, label.y.npc = 0.85) +
  # Axis labels and scales
  xlab(expression("Nitrate ("*mu*"g-N L"^{-1}*")")) +
  ylab(expression("Nitrogen fixation rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  scale_fill_manual(values = c("Mulholland et al. 2009" = ibm4[2], 
                               "Marcarelli et al. 2008" = ibm4[3])) +
  # Log scale
  scale_x_log10() +
  scale_y_log10() +
  coord_cartesian(ylim = c(1E-6, 1000), xlim = c(NA, 3000)) +
  # Theme adjustments
  theme_classic() +
  labs(tag = "b", fill = "Study") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = c(0.75, 0.85),
        legend.background = element_rect(color = "black"),
        legend.key.size = unit(0.15, 'in')) 

grob4 <- grid.arrange(a2, b2, nrow = 1)
ggsave(grob4, filename = "plots/NO3_DenitNfix_Scatter_sansCAREER.png", height = 5, 
       width = 10, units = "in", dpi = 300)
```

# Substrate plots

```{r boxplotAmDenit, fig.cap="Amended denitrification rates (n = 71) and nitrogen fixation rates (n = X) measured on multiple substrates and scaled to the stream reach based on percent abundance of substrate type in the reach. Vegetation = sum of algae and macrophyte cover. CWD = coarse woody debris. Boxplot error bars extend from the first quartile minus 1.5 times the interquartile range to the third quartile plus 1.5 times the interquartile range, middle bar denotes median.", fig.height=4, fig.width = 9, fig.fullwidth = T}
# Adjust formatting of substrate names
CAREER_scaledChamber$Substrate <- recode_factor(CAREER_scaledChamber$Substrate, 
                                                "bedrock" = "Bedrock", "CWD" = "Wood",
                                                "rock" = "Rock", "sediment" = "Sediment", 
                                                "leaf litter" = "Leaf litter",
                                                "vegetation" = "Vegetation")

# Boxplot of amended denitrification, by substrate
b <- 
  ggplot(data = subset(CAREER_scaledChamber, 
                       !is.na(DenitAmended_Mean_mgNm2hr_reachScaled)),
       aes(y = DenitAmended_Mean_mgNm2hr_reachScaled, x = Substrate)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(aes(fill = factor(Substrate)), outlier.shape = NA, width = 0.7) +
  geom_jitter(color = "black", size = 2, width = 0.2, shape = 21, fill = "white",
              alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Substrate type")) +
  ylab(expression("Denitrification patch rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "b") +
  scale_fill_manual(values = ibm4) +
  scale_x_discrete(limits = c("Sediment", "Vegetation", "Rock", "Wood")) +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

# Boxplot of N fixation, by substrate
c <- 
  ggplot(data = subset(CAREER_scaledChamber, !is.na(Nfix_Mean_mgNm2hr)),
       aes(y = Nfix_Mean_mgNm2hr_ReachScaled, x = Substrate)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(aes(fill = factor(Substrate)), outlier.shape = NA, width = 0.7) +
  geom_jitter(color = "black", size = 2, width = 0.2, shape = 21, fill = "white",
              alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Substrate type")) +
  ylab(expression("Nitrogen fixation patch rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "c") +
  scale_fill_manual(values = ibm4) +
  scale_x_discrete(limits = c("Vegetation", "Sediment", "Rock", "Wood")) +
  theme_classic() +
  theme(axis.text = element_text(color = "black", size = 8),
        axis.title = element_text(color = "black", size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

# Plot together
plot <- grid.arrange(a, b, c, nrow = 1) # amended
ggsave(plot, filename = "plots/ReachRates_BySubstrate.png", dpi = 300, width = 9, 
       height = 3, units = "in")
```

```{r boxplotAmendDIN, eval = FALSE, fig.cap="Amended denitrification rates (n = 71) and nitrogen fixation rates (n = X) measured on multiple substrates (macrophyte, rock, sediment, wood) present at each study site as part of the Marcarelli Nationwide Survey. Boxplot error bars extend from the first quartile minus 1.5 times the interquartile range to the third quartile plus 1.5 times the interquartile range, middle bar denotes median.", fig.height=8, fig.width = 6}
set.seed(11)
# Boxplots with colored points for [DIN]
# Boxplot of amended denitrification, by substrate
d <- 
  ggplot(data = subset(CAREER, !is.na(DenitAmended_Mean_mgNm2hr)),
       aes(y = DenitAmended_Mean_mgNm2hr, x = Substrate, fill = DIN_ugNL)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA, width = 0.7) +
  geom_jitter(color = "black", size = 2.5, width = 0.3, shape = 21, alpha = 0.9) +
  # Axis labels and scales
  xlab(expression("Substrate type")) +
  ylab(expression("Amended Denitrification rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "b", fill = expression("DIN ("*mu * g*"-N L"^{-1}*")")) +
  paletteer::scale_fill_paletteer_c("viridis::inferno") +
  scale_x_discrete(limits = c("Macrophyte", "Sediment", "Wood", "Rock")) +
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = c(0.23, 0.91),
        legend.background = element_rect(colour = "black"),
        legend.key.size = unit(0.15, 'in'))
set.seed(11)
# N Fix
f <- 
  ggplot(data = subset(CAREER, !is.na(Nfix_Mean_mgNm2hr)),
       aes(y = Nfix_Mean_mgNm2hr, x = Substrate, fill = DIN_ugNL)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(outlier.shape = NA, width = 0.7) +
  geom_jitter(color = "black", size = 2.5, width = 0.3, shape = 21, alpha = 0.9) +
  # Axis labels and scales
  xlab(expression("Substrate type")) +
  ylab(expression("Nitrogen fixation rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "c", fill = expression("DIN ("*mu * g*"-N L"^{-1}*")")) +
  paletteer::scale_fill_paletteer_c("viridis::inferno") +
  scale_x_discrete(limits = c("Macrophyte", "Sediment", "Wood", "Rock")) +
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none",
        legend.background = element_rect(colour = "black")) 

# Plot together
grob1 <- grid.arrange(d, f, nrow = 1) # amended
ggsave(grob1, filename = "plots/DenitNFix_Substrates.png", height = 8, 
       width = 7, units = "in", dpi = 300)

# both
#longways the data
rates_long <- CAREER %>%
  select(SiteName, date, DenitAmended_Mean_mgNm2hr, Nfix_Mean_mgNm2hr) %>%
  pivot_longer(cols = 3:4, names_to = "process")

o <- 
  ggplot(data = rates_long) +
  geom_jitter(aes(y = value, x = process, fill = process), shape = 21, 
              size =2.5, width = 0.2, alpha = 0.9) +
  # Axis labels and scales
  xlab(expression("Process")) +
  ylab(expression("Denitrification or Nitrogen fixation rate (mg-N"~m^{-2}~"hr"^{-1}*")")) +
  labs(tag = "a") +
  scale_fill_manual(values = ibm2) +
  scale_x_discrete(labels = c(DenitAmended_Mean_mgNm2hr = "Amended\ndenitrification", 
                              Nfix_Mean_mgNm2hr = "Nitrogen\nfixation")) +
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none",
        legend.background = element_rect(colour = "black")) 

d2 <- d + theme(legend.position = c(0.2, 0.91))

grob2 <- grid.arrange(o, d2, f, nrow = 1, layout_matrix = rbind(c(1,2,2,3,3)))
ggsave(grob2, filename = "plots/DenitNFix_Substrates_2.png", height = 8, 
       width = 10, units = "in", dpi = 300)
```

# Comparisons between CAREER and LINX II datasets

```{r DIN2, eval = FALSE, fig.cap="Distribution of DIN concentrations in CAREER and LINX II study. Omitted one datapoint from LINXII where DIN = 21165 ugL because it squished the axis. need to fix", fig.height=6, fig.width=3}
f <- ggplot(data, aes(y = DIN_ugNL, x = Project, fill = Project)) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("DIN ug-N / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 5000)) +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 
f
```

```{r DIN3, eval = F, fig.cap="Distribution of DIN concentrations in CAREER and LINX II study. Omitted one datapoint from LINXII where DIN = 21165 ugL because it squished the axis. need to fix", fig.height=6, fig.width=4}
f2 <- f + labs(tag = "b")
#these NP numbers aren't right, they should be TN / TP, currently DIN / TP
g <- ggplot(data = CAREER_sites, 
       aes(y = NP_molar_DINTDP, x = Project, fill = Project)) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("N:P (DIN / TP)")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "a") +
  #coord_cartesian(ylim = c(0, 5000)) +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 
grid.arrange(g, f2, nrow = 1, layout_matrix = rbind(c(1,2,2)))
```

```{r N1, eval = FALSE, fig.height=10, fig.width = 8.5}
h <- ggplot(data = CAREER, aes(y = TDN_mgL, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("TDN mg-N / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "a") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

i <- ggplot(data = CAREER, aes(y = NH4_ugL, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("NH4 ugN / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "b") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

j <- ggplot(data = CAREER, aes(y = NO2NO3_ugL, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("NO2 + NO3 ugN / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "c") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

k <- ggplot(data = CAREER, aes(y = SRP_ugL, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("SRP ug / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "d") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

l <- ggplot(data = CAREER, aes(y = TDP_ugL, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("TDP ug / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "e") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

m <- ggplot(data = CAREER, aes(y = TP_ugL, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("TP ug / L")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  labs(tag = "f") +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 

grid.arrange(h, i, j, k, l, m, nrow = 3)
```

```{r N2, eval = FALSE, fig.height=6, fig.width = 8.5}
CAREER_sites$TP_mgL <- CAREER_sites$TP_ugL / 1000
CAREER_sites$NP_TDN.TP <- CAREER_sites$TDN_mgL / CAREER_sites$TP_mgL

ggplot(data = CAREER_sites, aes(y = NP_TDN.TP, x = Organization, 
                          fill = Organization)) +
  # Labels
  geom_label(aes(label = SiteName), hjust = 0, fill = "white", nudge_x = 0.1,
             size = 3) +
  # Career sites
  geom_point(color = "black", size = 3, shape = 21, alpha = 0.7) +
  # Axis labels and scales
  xlab(expression("Study")) +
  ylab(expression("N:P (as TDN/TP)")) +
  scale_fill_manual(values = ibm4) +
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        axis.text.y = element_text(size = 8),
        panel.background = element_rect(color = "black"), 
        legend.position = "none") 
```

```{r table, eval = FALSE}
# Order NP from low to high
sortNP <- order(CAREER_sites$NP_molar_DINTDP)

tabledata <- data.frame(SiteName = CAREER_sites$SiteName[sortNP],
                        SampleDate = CAREER_sites$date[sortNP],
                        State = CAREER_sites$State[sortNP],
                        Organization = CAREER_sites$Organization[sortNP],
                        NPmolar_asDIN.TDP = CAREER_sites$NP_molar_DINTDP[sortNP],
                        DIN_ugL = CAREER_sites$DIN_ugNL[sortNP],
                        NH4_ugL = CAREER_sites$NH4_ugL[sortNP],
                        NO2NO3_ugL = CAREER_sites$NO2NO3_ugL[sortNP],
                        SRP_ugL = CAREER_sites$SRP_ugL[sortNP],
                        TDP_ugL = CAREER_sites$TDP_ugL[sortNP])

knitr::kable(tabledata, booktabs = T) %>% kable_styling(latex_options = c("striped", "scale_down"))
```





# Site maps

## CAREER sites

```{r map_allCAREERsites, fig.cap="Map of all CAREER study sites (n = 30).", fig.height=7, fig.width=7, fig.fullwidth = T}
##### Plot CAREER Site Map #####
# Pull state map data
world.map <- map_data("world") 
states.map <- map_data("state")

# Subset distinct sites
sites <- 
  CAREER_sites %>% 
  select(SiteName, Organization, Latitude, Longitude) %>% 
  distinct(SiteName, .keep_all = TRUE) 

# Continental US
map_continentalUS <- 
  ggplot() +
  # State and country outlines
  geom_polygon(data = world.map, aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  geom_polygon(data = states.map, aes(x = long, y = lat, group = group), 
               color = "grey", size = 0.2, fill = NA) +
  geom_polygon(data = subset(world.map, region == "USA"), 
               aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  # Location markers and labels
  #geom_text_repel(data = filter(sites, Longitude < -70), 
   #               aes(x = Longitude, y = Latitude, 
    #                  label = rownames(filter(sites, Longitude < -70))), 
     #              size = 3, segment.color = "black") +
  # Location markers
  geom_point(data = sites, aes(x = Longitude, y = Latitude, 
                                      fill = Organization), 
             shape = 21, size = 3, color = "black", alpha = 0.7) +
  # Coordinates
  coord_map(projection = "azequalarea",
            xlim = c(-115,-80), ylim = c(15, 67)) +
  # Axis labels
  xlab("Longitude") +
  ylab("Latitude") +
  # Theme adjustments
  theme_classic() +
  labs(tag = "a") +
  theme(legend.direction ="vertical", 
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.key.height = unit(0.25, 'cm'),
        legend.position = c(0.15, 0.1),
        axis.text = element_text(color = "black", size = 10),
        axis.title = element_text(size = 12),
        panel.background = element_rect(color = "black"),
        panel.grid = element_line(color = "red")) +
  scale_fill_manual(values = ibm4) +
  scale_color_manual(values = ibm4) 

# Alaska
map_alaska <- 
  ggplot() +
  # State and country outlines
  geom_polygon(data = world.map, aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  coord_map(projection = "azequalarea",
            xlim = c(-175,-135), ylim = c(50, 75)) +
  geom_polygon(data = states.map, aes(x = long, y = lat, group = group), 
               color = "grey", size = 0.2, fill = NA) +
  geom_polygon(data = subset(world.map, region == "USA"), 
               aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  # Location markers and labels
  #geom_label_repel(data = sites, aes(x = Longitude, y = Latitude, 
   #                                  label = rownames(sites)), 
    #               size = 3, segment.color = "black", 
     #              label.size = 0.6) +
  # Location markers
  geom_point(data = sites, aes(x = Longitude, y = Latitude, 
                                      fill = Organization), 
             shape = 21, size = 3, color = "black", alpha = 0.7) +
  # Theme adjustments
  theme_classic() +
  labs(tag = "b") +
  theme(legend.direction ="vertical", 
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.key.height = unit(2, 'cm'),
        axis.text = element_text(color = "black", size = 10),
        axis.title = element_blank(),
        panel.background = element_rect(color = "black")) +
  scale_fill_manual(values = ibm4) +
  scale_color_manual(values = ibm4) +
  guides(fill = "none")

# Puerto Rico
map_pr <- 
  ggplot() +
  # State and country outlines
  geom_polygon(data = world.map, aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  coord_map(projection = "azequalarea",
            xlim = c(-68,-65), ylim = c(17, 19)) +
  geom_polygon(data = states.map, aes(x = long, y = lat, group = group), 
               color = "grey", size = 0.2, fill = NA) +
  geom_polygon(data = subset(world.map, region == "USA"), 
               aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  # Location markers and labels
  #geom_text_repel(data = filter(sites, Longitude > -70), 
   #               aes(x = Longitude, y = Latitude, 
    #                  label = rownames(filter(sites, Longitude > -70))), 
     #              size = 3, segment.color = "black") +
  # Location markers
  geom_point(data = sites, aes(x = Longitude, y = Latitude, 
                                      fill = Organization), 
             shape = 21, size = 3, color = "black", alpha = 0.7) +
  # Theme adjustments
  theme_classic() +
  labs(tag = "c") +
  theme(axis.text = element_text(color = "black", size = 10),
        axis.title = element_blank(),
        panel.background = element_rect(color = "black")) +
  scale_fill_manual(values = ibm4) +
  scale_color_manual(values = ibm4) +
  guides(fill = "none")

# Combine maps into a single plot
grob <- 
  ggdraw() +
  draw_plot(map_continentalUS) +
  draw_plot(map_alaska, x = 0.15, y = 0.67, width = 0.3, height = 0.3) +
  draw_plot(map_pr, x = 0.62, y = 0.02, width = 0.3, height = 0.3)

ggsave(grob, filename = "plots/Map_CAREERInlay.png", width = 7, height = 7, 
       units = "in", dpi = 300)

grob
```



```{r map_NEONsites, eval = F, fig.cap="Map of NEON study sites.", fig.height=6, fig.width=10, fig.fullwidth = T}
##### Plot CAREER Site Map #####
# Pull state map data
world.map <- map_data("world")
states.map <- map_data("state")

NEON_sites <- subset(CAREER_sites, Organization == "NEON") %>% 
  distinct(SiteName, .keep_all = TRUE)

# Plot map
ggplot() +
  # State and country outlines
  geom_polygon(data = world.map, aes(x = long, y = lat, group = group), 
               color = "grey", size = 0.2, fill = NA) +
  geom_polygon(data = states.map, aes(x = long, y = lat, group = group), 
               color = "grey", size = 0.2, fill = NA) +
  geom_polygon(data = subset(world.map, region == "USA"), 
               aes(x = long, y = lat, group = group), 
               color = "black", size = 0.2, fill = NA) +
  # Location markers and labels
  geom_label_repel(data = NEON_sites %>% 
                     select(SiteName, Latitude, Longitude) %>% 
                     distinct(SiteName, .keep_all = TRUE), 
                   aes(x = Longitude, y = Latitude, label = SiteName), 
                   box.padding = 0.6, size = 2, nudge_x = 0.01, 
                   segment.size = 0.2, segment.color = "black", 
                   label.size = 0.4) +
  geom_point(data = NEON_sites %>% 
                     select(SiteName, Latitude, Longitude) %>% 
                     distinct(SiteName, .keep_all = TRUE), 
             aes(x = Longitude, y = Latitude), 
             shape = 21, fill = "#FFB000",
             color = "black", size = 3, stroke = 1) +
  coord_fixed(1.3, xlim = c(-180,-30), ylim = c(10, 75)) +
  # Theme adjustments
  theme_nothing() +
  theme(panel.background = element_rect(color = "black", fill = "white")) +
  scale_fill_manual(values = ibm4) +
  guides(fill = "none")

ggsave(filename = "plots/NEONSitesMap.png", width = 4, height = 2, 
       units = "in", dpi = 400)
```

# Metabolism

```{r plotNEPmonthlymean, eval = F, fig.cap="Time series data of daily NEP (grey lines) and calculated mean NEP for each day of year (colored lines, A), and calculated mean monthly NEP (B) for the period of record. Shaded ribbons (B) represent standard deviation of NEP.", fig.height=5.5, fig.width = 8}
# West to east order of sites
# filter out non-annual siteso
      # hop brook
      # blaine creek 
      # prieta stream
      # mcrae (needs rerun)

metabPlot <- 
  CAREER_sites %>%
  select(SiteName, Longitude, date) %>%
  mutate(year = year(date)) %>%
  rename(samplingDate = date) %>%
  full_join(., CAREER_metabolism) %>%
  filter(!SiteName %in% c("Hop Brook", "Blaine Creek", "Prieta Stream", "McRae Creek",
                          "1300 E Red Butte Creek", "Lower Knowton Fork Red Butte Creek",
                          "Kings Creek", "Hubbard Brook", "Sonadora Stream", "Alexander Springs",
                          "South Fork Mink Creek", "Caribou Creek"))

# add in a day of year column
metabPlot$doy <- yday(metabPlot$date)
metabPlot$year <- year(metabPlot$date)
#Factorize site name by latitude
metabPlot$SiteName <- reorder(metabPlot$SiteName, metabPlot$Longitude)

# Plot of DOY vs GPP or ER, faceted by site
#a <- 
  ggplot(data = CAREER_metabolism) +
  # Facet wrap plots
  facet_wrap(~SiteName, nrow = 3) +
  # Lines for all years of data
  geom_line(aes(x = DOY, y = NEP, linetype = year), color = "darkgrey", alpha = 0.7) +
  # Lines for mean data
  geom_line(data = modelResults_DOY, aes(x = DOY, y = NEP_mean, color = site)) +
  geom_hline(yintercept = 0, linetype = 2) +
  # Axis labels and scales
  ylab(expression("NEP (g"~O[2]~m^2~"d"^{-1}*")")) +
  xlab("Day of year") +
  labs(tag = "A") +
  # Remove legend for site
  guides(color = FALSE, linetype = guide_legend(nrow = 3, title = "Year")) +
  # Theme adjustments
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        panel.background = element_rect(color = "black"),
        legend.position = "bottom") +
  # Color scales
  scale_color_brewer(palette = 2, type = "qual")

# Plot of average NEP by month, all sites on one plot
b <- 
  ggplot(data = modelResults_monthly, aes(x = month, group = site)) +
  # Ribbon for visualizing standard error
  geom_ribbon(aes(ymin = NEP_mean-NEP_sd, 
                  ymax = NEP_mean+NEP_sd, fill = site), alpha = 0.1)+
  # Line and points for mean NEP
  geom_line(aes(y = NEP_mean, color = site)) +
  geom_point(aes(y = NEP_mean, color = site), 
             shape = 21, fill = "white", size = 2) +
  # Horizontal line at y = 0
  geom_hline(yintercept = 0, linetype = 2) +
  # Axis labels and scales
  labs(tag = "B", fill = "Site", color = "Site") +
  ylab(expression("NEP (g"~O[2]~m^2~"d"^{-1}*")")) +
  xlab("Day of year") +
  # Theme adjustments
  guides(color = guide_legend(nrow = 3), fill = guide_legend(nrow = 3))+
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        panel.background = element_rect(color = "black"), 
        legend.position = "bottom") +
  # Color scales
  scale_color_brewer(palette = 2, type = "qual") +
  scale_fill_brewer(palette = 2, type = "qual")

grid.arrange(a,b, ncol = 2)
```

```{r plotNEPloess, eval = F, fig.cap="Time series data of daily NEP (grey lines) and calculated mean NEP for each day of year (colored lines, A), and annual trends in NEP over the period of record visualized using local polynomial regression fitting (LOESS, B). Shaded ribbons (B) represent 95% confidence interval on LOESS estimate.", fig.height=5.5, fig.width = 8}
# Plot of DOY vs GPP or ER, faceted by site
c <- 
  ggplot(data = NULL) +
  # Facet wrap plots
  facet_wrap(~site, nrow = 3) +
  # Lines for all years of data
  geom_line(data = modelResults_all, aes(x = DOY, y = NEP, linetype = year), color = "darkgrey", alpha = 0.7) +
  # Lines for mean data
  geom_line(data = modelResults_DOY, aes(x = DOY, y = NEP_mean, color = site)) +
  
  geom_hline(yintercept = 0, linetype = 2) +
  # Axis labels and scales
  ylab(expression("NEP (g"~O[2]~m^2~"d"^{-1}*")")) +
  xlab("Day of year") +
  labs(tag = "A") +
  # Remove legend for site
  guides(color = FALSE, linetype = guide_legend(nrow = 3, title = "Year")) +
  # Theme adjustments
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        panel.background = element_rect(color = "black"),
        legend.position = "bottom") +
  # Color scales
  scale_color_brewer(palette = 2, type = "qual")

# LOESS smooth
d <- 
  ggplot(data = modelResults_all, aes(x = DOY, y = NEP)) +
  stat_smooth(aes(color = site, fill = site), method = "loess") +
  # Horizontal line at y = 0
  geom_hline(yintercept = 0, linetype = 2) +
  # Axis labels and scales
  labs(tag = "B", fill = "Site", color = "Site") +
  ylab(expression("NEP (g"~O[2]~m^2~"d"^{-1}*")")) +
  xlab("Month") +
  # Theme adjustments
  guides(color = guide_legend(nrow = 3), fill = guide_legend(nrow = 3))+
  theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        panel.background = element_rect(color = "black"), 
        legend.position = "bottom") +
  # Color scales
  scale_color_brewer(palette = 2, type = "qual") +
  scale_fill_brewer(palette = 2, type = "qual")

grid.arrange(c,d, ncol = 2)



# Compute PCA of metabolism data
#prcomp(modelResults_all[,c(3,6,12,13)], center = T, scale. = T)


#modelResults_all %>%
 # select(GPP, ER, NEP, DOY)

# Compute Kmediods using pam (Partitioning Around Medoids) from cluster
#collsub_kmediods <- pam(colleges_sub, k = 3)
# For K-mediods results
#fviz_cluster(collsub_kmediods, data = colleges_sub) + 
 # labs(tag = "B", title = "K-mediods clustering") +
#  theme_classic() +
#  theme(legend.position = "none")
```

```{r supplemental table: K600 priors for neon sites}
params <- read_csv("data/metabolism/metabolism-parameters.csv")

# If any 0s in depth, K600.est will be Inf, change to NA
params$K600.estimate[is.infinite(params$K600.estimate)] <- NA

neonsites <- filter(CAREER_sites, Organization == "NEON")

# K600 priors were the log10 mean of the K600 estimates of that day
k600priors <-
  params %>%
  group_by(SiteName, date) %>%
  summarise(Q_Ls = round(mean(discharge, na.rm = TRUE)*1000, 3),
            K600_d = round(mean(K600.estimate, na.rm = TRUE), 3)) %>%
  #filter(!is.nan(K600)) %>%
  arrange(SiteName, date) %>%
  filter(SiteName %in% neonsites$SiteName)

write_csv(k600priors, "outputs/supplemental_table_estimated-k600.csv")
```

```{r supplemental table: metabolism modeling results}
metab <- read_csv("data/metabolism/metabolism-rates.csv")

metab_table <- 
  metab %>%
  group_by(SiteName, date) %>%
  select(SiteName, date, 
         GPP_daily_mean, GPP_daily_sd, GPP_daily_Rhat,
         ER_daily_mean, ER_daily_sd, ER_daily_Rhat,
         K600_daily_mean, K600_daily_sd, K600_daily_Rhat,
         DO_R2_mean, DO_R2_sd, DO_R2_Rhat) %>%
  transmute(date = as.character(date),
            GPP = paste0(round(GPP_daily_mean, 3), " (±", 
                         round(GPP_daily_sd, 3), ")"),
            ER = paste0(round(ER_daily_mean, 3), " (±", 
                         round(ER_daily_sd, 3), ")"),
            K600 = paste0(round(K600_daily_mean, 3), " (±", 
                         round(K600_daily_sd, 3), ")"),
            DO_R2 = paste0(round(DO_R2_mean, 3), " (±", 
                         round(DO_R2_sd, 3), ")"),
            Rhat_GPP = round(GPP_daily_Rhat, 3),
            Rhat_ER = round(ER_daily_Rhat, 3),
            Rhat_K600 = round(K600_daily_Rhat, 3)) %>%
  arrange(SiteName, date)

write_csv(metab_table, "outputs/supplemental_table_metabolism-rates.csv")
```
